# Test Space


```{r setup, include=FALSE}
image.dir<- here::here("docs/images")
#Default Rmd options
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = 'center', 
                      fig.path = "docs/images/") #allows for inserting R code into captions

#Plotting and data libraries
library(ggplot2)
library(dplyr)
library(tidyr)
library(ecodata)
library(here)
library(kableExtra)
library(ggrepel)
library(stringr)
library(patchwork)
library(grid)
library(heatwaveR)
library(stringr)

#General inline text input for report

#Council
council <- "Mid-Atlantic Fishery Management Council"
council_abbr <- "MAFMC"

#Region identifiers
epu <- "Mid-Atlantic Bight"
epu_abbr <- "MAB"
region <- "Mid-Atlantic"
region_abbr <- "MA" #Some commercial data organized by "MA" or "NE" regions, not by EPU 

############################# GIS SETUP ######################################################

#GIS libraries
library(sf)
library(rgdal)
library(raster)
#CRS
crs <- "+proj=longlat +lat_1=35 +lat_2=45 +lat_0=40 +lon_0=-77 +x_0=0 +y_0=0 +datum=NAD83 +no_defs +ellps=GRS80 +towgs84=0,0,0"

#EPU shapefile
epu_sf <- ecodata::epu_sf %>% 
  filter(EPU %in% c("MAB","GB","GOM"))

#Map line parameters
map.lwd <- 0.4

# Set lat/lon window for maps
xmin = -77
xmax = -65
ymin = 36
ymax = 45
xlims <- c(xmin, xmax)
ylims <- c(ymin, ymax)

#Time series constants
shade.alpha <- 0.3
shade.fill <- "lightgrey"
lwd <- 1
pcex <- 2
trend.alpha <- 0.5
trend.size <- 2
hline.size <- 1
hline.alpha <- 0.35
hline.lty <- "dashed"
label.size <- 5
hjust.label <- 1.5
letter_size <- 4
feeding.guilds <- c("Apex Predator","Piscivore","Planktivore","Benthivore","Benthos")
x.shade.min <- 2011
x.shade.max <- 2021
#Function for custom ggplot facet labels
label <- function(variable,value){
  return(facet_names[value])
}

```


Trend lines are shown when slope is significantly different from 0 at the p < 0.05 level. An orange line signifies an overall positive trend, and purple signifies a negative trend. Note that in the final report we will only test for trend when N >= 30. However, I have relaxed that requirement for the purposes of this document so that trends are highlighted when N >= 20. **This means that some trends shown here will not be present in the final document**. Dashed lines represent mean values of time series unless the indicator is an anomaly, in which case the dashed line is equal to 0. Shaded regions indicate the past ten years. If there are no new data for 2018, the shaded region will still cover this time period.

## Mid-Atlantic Bight

### Ocean Temperature {.tabset .tabset-fade}

#### SST

```{r seasonal-sst-anom-gridded, fig.cap="MAB seasonal sea surface temperature time series overlaid onto 2021 seasonal spatial anomalies."}
annotation_custom2 <- function (data, ...)
{
  layer(data = data,
        stat = "identity",
        position = "identity",
        geom = ggplot2:::GeomCustomAnn,
        inherit.aes = FALSE,
        params = list(...))
}

#EPU shapefile
mab_epu_sf <- ecodata::epu_sf %>% 
  dplyr::filter(EPU %in% c("MAB")) 

#Map line parameters
map.lwd <- 0.4

# Set lat/lon window for maps
xmin = -81
xmax = -66
ymin = 35.5
ymax = 43
xlims <- c(xmin, xmax)
ylims <- c(ymin, ymax)
sst <- ecodata::seasonal_sst_anomaly_gridded 

sst$Season <- factor(sst$Season, levels = c("Winter",
                                            "Spring",
                                            "Summer",
                                            "Fall"))
# ma_anom<-ecodata::seasonal_oisst_anom
# 
# ma_anom$Var <- factor(ma_anom$Var, levels= c("Winter","Spring","Summer","Fall"))
sst<- sst %>% dplyr::mutate(Value = replace(Value, Value > 4, 4))

#functions
sst_map <- function(season){
  ggplot2::ggplot(sst %>%
                    dplyr::filter(Season == season)) +
  ggplot2::geom_tile(aes(x = Longitude, y = Latitude,fill = Value)) +
  ggplot2::geom_sf(data = ecodata::coast, size = map.lwd) +
  ggplot2::geom_sf(data = mab_epu_sf, fill = "transparent", size = map.lwd) +
  ggplot2::scale_fill_gradient2(name = "Temp.\nAnomaly (C)",
                       low = scales::muted("blue"),
                       mid = "white",
                       high = scales::muted("red"),
                       limits = c(-4,4),
                       labels = c("<-4", "-2", "0", "2", ">4")) +
  ggplot2::coord_sf(crs = crs, xlim = xlims, ylim = ylims) +
  #ggplot2::facet_wrap(Season~.) +
  ecodata::theme_map() +
  ggplot2::ggtitle(season) +
  ggplot2::xlab("Longitude") +
  ggplot2::ylab("Latitude") +
  ggplot2::theme(panel.border = element_rect(colour = "black", fill=NA, size=0.75),
        legend.key = element_blank(),
        axis.title = element_text(size = 11),
        strip.background = element_blank(),
        strip.text=element_text(hjust=0),
        axis.text = element_text(size = 8), 
        axis.title.y = element_text(angle = 90))+
  ecodata::theme_title()
}

season_anom <- function(season){
  ggplot2::ggplotGrob( ecodata::seasonal_oisst_anom %>% 
                              dplyr::filter(EPU == "MAB",
                                     stringr::str_detect(Var, season)) %>% 
                              dplyr::mutate(hline = mean(Value)) %>% 
                              ggplot2::ggplot(aes(x = Time, y = Value)) +
                              ggplot2::annotate("rect", fill = shade.fill, alpha = shade.alpha,
                                       xmin = x.shade.min , xmax = x.shade.max,
                                       ymin = -Inf, ymax = Inf) +
                              ggplot2::geom_line() +
                              ggplot2::geom_point() +
                              ecodata::geom_gls(alpha = trend.alpha + 0.25) +
                              ggplot2::ylab("SST anomaly (C)")+
                              ggplot2::xlab(element_blank())+
                              ggplot2::scale_x_continuous(expand = c(0.01, 0.01)) +
                              ggplot2::geom_hline(aes(yintercept = hline)) +
                              ecodata::theme_ts()+
                              ggplot2::theme(axis.title = element_text(size = 6),
                                    axis.text = element_text(size = 6),
                                    panel.background = element_rect(fill = "transparent"), 
                                    plot.background = element_rect(fill = "transparent", color = NA), 
                                    panel.grid.major = element_blank(),
                                    panel.grid.minor = element_blank(), 
                                    legend.background = element_rect(fill = "transparent"), 
                                    legend.box.background = element_rect(fill = "transparent"), 
                                    legend.key = element_rect(fill = "transparent", colour = NA), 
                                    axis.line = element_blank(),
                                    panel.border = element_blank())
  )
}

# create anomaly grobs
winter_anom <- season_anom(season = "Winter")

spring_anom <- season_anom(season = "Spring")

summer_anom <- season_anom(season = "Summer")

fall_anom <- season_anom(season = "Fall")

# create plots for each season
winter <- sst_map(season = "Winter") +
  annotation_custom2(grob = winter_anom,  xmin=-82, xmax=-73.75,
                     ymin=39, ymax=43.5, data = data.frame(Season = "Winter"))

spring <- sst_map(season = "Spring") +
  annotation_custom2(grob = spring_anom,  xmin=-82, xmax=-73.75,
                   ymin=39, ymax=43.5, data = data.frame(Season = "Spring"))

summer <- sst_map(season = "Summer") +
  annotation_custom2(grob = summer_anom,  xmin=-82, xmax=-73.75,
                   ymin=39, ymax=43.5, data = data.frame(Season = "Summer"))

fall <- sst_map(season = "Fall") +
  annotation_custom2(grob = fall_anom,  xmin=-82, xmax=-73.75,
                   ymin=39, ymax=43.5, data = data.frame(Season = "Fall"))

# arrange
ggpubr::ggarrange(winter, spring, summer, fall,
                  ncol = 2,
                  nrow = 2,
                  common.legend = TRUE,
                  legend = "right") %>%
  ggpubr::annotate_figure(top = "SST anomaly (2021)")

```
